---
title: "Resume Study_Check Raw Data"
output:
    html_document:
        toc: true
        toc_float: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Load packages

library(tidyverse)
library(lubridate)

# Import raw data

dat_res <- read_rds("Resume-Study_Data/res-level_raw.rds")

dat_post <- read_rds("Resume-Study_Data/post-level_raw.rds")
```

# Resume level data

## Check for correct markings of "error"

```{r}
# Number of resumes with "error" in the comment
dat_res %>%
filter(str_detect(cmt, "error")) %>%
nrow()

# Check for posts with only one resume marked as "error"
dat_res %>%
filter(str_detect(cmt, "error")) %>%
count(post_id) %>%
filter(n != 2)
```

## Data manipulation

```{r}
# Exclude non-usable posts
dat_res <- dat_res %>%
filter(!str_detect(cmt, "error"))

# Replace empty strings with NA

dat_res <- dat_res %>%
mutate(across(where(is.character), ~ na_if(., "")))

dat_post <- dat_post %>%
mutate(across(where(is.character), ~ na_if(., "")))

# Recode response variables
dat_res <- dat_res %>%
mutate(
    rsp = case_when(
        is.na(rsp) ~ "no",
        TRUE ~ rsp
    ),
    rsp_call = case_when(
        is.na(rsp_call) ~ "no",
        TRUE ~ rsp_call
    ),
    rsp_wechat = case_when(
        is.na(rsp_wechat) ~ "no",
        TRUE ~ rsp_wechat
    )
)

# Construction of time variables
dat_res <- dat_res %>%
mutate(
    subtime2 = case_when(
        as.numeric(substr(subday, 1, 2)) < 9
        ~ ymd_hms(paste0("2025", subday, subtime, "00")),
        TRUE ~ ymd_hms(paste0("2024", subday, subtime, "00"))
    ),
    rsp_time2 = case_when(
        as.numeric(substr(rsp_day, 1, 2)) < 9
        ~ ymd_hms(paste0("2025", rsp_day, rsp_time, "00")),
        TRUE ~ ymd_hms(paste0("2024", rsp_day, rsp_time, "00"))
    ),
    sub_year = year(subtime2),
    sub_month = month(subtime2, label = TRUE),
    sub_wday = wday(subtime2, label = TRUE),
    sub_hour = hour(subtime2),
    rsp_year = year(rsp_time2),
    rsp_month = month(rsp_time2, label = TRUE),
    rsp_wday = wday(rsp_time2, label = TRUE),
    rsp_hour = hour(rsp_time2)
)
```

## Check for correct markings of "error" (after exclusion)

```{r}
# Number of resumes with "error" in the comment
dat_res %>%
filter(str_detect(cmt, "error")) %>%
nrow()

# Check for posts with only one resume marked as "error"
dat_res %>%
filter(str_detect(cmt, "error")) %>%
count(post_id) %>%
filter(n != 2)
```

## Variable values

```{r}
duplicated(dat_res$res_id) %>% sum()

duplicated(dat_res$post_id) %>% sum()

count(dat_res, post_id) %>% filter(n != 2)

count(dat_res, sub_order)

count(dat_res, res_type)

count(dat_res, res_type, sub_order)

count(dat_res, pcat)

count(dat_res, pcity)
```

## Check for mismatches of `post_id` between the two data sets

```{r}
dat_res %>%
anti_join(dat_post, by = "post_id") %>%
select(res_id, post_id, pcity)
```

## Check for anomalies in time variables

```{r}
# 1. NAs in subday and subtime
dat_res %>%
    filter(is.na(subday) | is.na(subtime)) %>%
    select(res_id, pcity, subday, subtime)

# 2. Check that all time variables have the correct string length (4):
dat_res %>%
    filter(nchar(subday) != 4 | nchar(subtime) != 4 |
                 nchar(rsp_day) != 4 | nchar(rsp_time) != 4) %>%
    select(res_id, pcity, subday, subtime, rsp_day, rsp_time)

# 3. Check valid range for subday (date in 2024-09-09 to 2025-02-25)

# Helper function: convert mmdd string to a Date (2024 if month>=9, else 2025)
convert_mmdd <- function(x, thresh_month = 9,
year_before = 2024, year_after = 2025) {
  month_val <- as.integer(substr(x, 1, 2))
  day_val <- substr(x, 3, 4)
  year_use <- ifelse(month_val >= thresh_month, year_before, year_after)
  as.Date(sprintf("%d-%02d-%s", year_use, month_val, day_val))
}

dat_res <- dat_res %>% mutate(subday_date = convert_mmdd(subday))

dat_res %>%
  filter(subday_date < as.Date("2024-09-09") |
  subday_date > as.Date("2025-02-25")) %>%
  select(res_id, pcity, subday, subday_date)

# 4. Check valid range for rsp_day (date in 2024-09-09 to 2025-03-01)
dat_res <- dat_res %>% mutate(rsp_day_date = convert_mmdd(rsp_day))

dat_res %>%
  filter(rsp_day_date < as.Date("2024-09-09") |
  rsp_day_date > as.Date("2025-03-01")) %>%
  select(res_id, pcity, rsp_day, rsp_day_date)

# 5. Check valid range for subtime and rsp_time (numeric between 0000 and 2400)
dat_res <- dat_res %>%
  mutate(subtime_num = as.numeric(subtime),
         rsp_time_num = as.numeric(rsp_time))

dat_res %>%
  filter(subtime_num < 0 | subtime_num > 2400) %>%
  select(res_id, pcity, subtime, subtime_num)

dat_res %>%
  filter(rsp_time_num < 0 | rsp_time_num > 2400) %>%
  select(res_id, pcity, rsp_time, rsp_time_num)

# 6. rsp_time2 should be after sub_time2
dat_res %>%
  filter(subtime2 > rsp_time2) %>%
  select(res_id, pcity, subtime2, rsp_time2)
```

## Check for balance of time variables

```{r}
iwalk(select(dat_res, sub_year:rsp_hour), ~ {
  cat("Column:", .y, "\n")
  print(count(data.frame(x = .x), x, .drop = FALSE))
  cat("\n")
})
```

## Check for response variables

```{r}
# Distribution of response status
count(dat_res, rsp, sub_order)

# Check for inconsistencies between `rsp` and `rsp_msg`
dat_res %>%
filter((rsp == "no" & !is.na(rsp_msg)) | (rsp == "yes" & is.na(rsp_msg))) %>%
select(res_id, pcity, rsp)

# Check for inconsistencies between `rsp` and `rsp_cat`
dat_res %>%
filter(rsp == "no", !is.na(rsp_cat)) %>%
select(res_id, pcity, rsp, rsp_cat)

# Check for inconsistencies between `rsp` and `rsp_call`
dat_res %>%
filter(rsp == "no", rsp_call != "no") %>%
select(res_id, pcity, rsp, rsp_call)

# Check for inconsistencies between `rsp` and `rsp_wechat`
dat_res %>%
filter(rsp == "no", rsp_wechat != "no") %>%
select(res_id, pcity, rsp, rsp_wechat)

# Incorrect values for `rsp_call` and `rsp_wechat`
dat_res %>%
filter(!rsp_call %in% c("yes", "no") | !rsp_wechat %in% c("yes", "no")) %>%
select(res_id, pcity)
```

## Cross check `rsp_cat`

```{r}
proc_cat_gd <- dat_res %>%
filter(rsp == "yes", res_id <= 3000) %>%
select(res_id, post_id, pcity, rsp, rsp_call, rsp_wechat, cmt, rsp_msg, rsp_cat)

proc_cat_bj <- dat_res %>%
filter(rsp == "yes", res_id > 3000, res_id <= 6000) %>%
select(res_id, post_id, pcity, rsp, rsp_call, rsp_wechat, cmt, rsp_msg, rsp_cat)

proc_cat_sh <- dat_res %>%
filter(rsp == "yes", res_id > 6000) %>%
select(res_id, post_id, pcity, rsp, rsp_call, rsp_wechat, cmt, rsp_msg, rsp_cat)

haven::write_sav(proc_cat_gd, "proc_cat_gd.sav")
haven::write_sav(proc_cat_bj, "proc_cat_bj.sav")
haven::write_sav(proc_cat_sh, "proc_cat_sh.sav")
```

# Post level data

## Data manipulation

```{r}
# Replace empty strings with NA
dat_post <- dat_post %>%
mutate(across(where(is.character), ~ na_if(., "")))
```

## Variable values

```{r}
duplicated(dat_post$post_id) %>% sum()

count(dat_post, post_id) %>% filter(n != 1)

count(dat_post, preg) %>% arrange(desc(n))

count(dat_post, pcat) %>% arrange(desc(n))

count(dat_post, pcity) %>% arrange(desc(n))

count(dat_post, pexp) %>% arrange(desc(n))

count(dat_post, pedu) %>% arrange(desc(n))

count(dat_post, psal_lower) %>% arrange(desc(n))

count(dat_post, psal_upper) %>% arrange(desc(n))

count(dat_post, psal_mon) %>% arrange(desc(n))

dat_post %>% filter(pcandno <= 0) %>% select(post_id, pcandno)

count(dat_post, flogo) %>% arrange(desc(n))

count(dat_post, fsize) %>% arrange(desc(n))

count(dat_post, ffinc) %>% arrange(desc(n))

dat_post %>% filter(fpostno <= 0) %>% select(post_id, fpostno)

dat_post %>% filter(fhrno <= 0) %>% select(post_id, fhrno)

count(dat_post, fcat) %>% arrange(desc(n))

count(dat_post, fcap) %>% arrange(desc(n))

count(dat_post, fhour) %>% arrange(desc(n))

count(dat_post, fdayoff) %>% arrange(desc(n))

count(dat_post, falbum) %>% arrange(desc(n))

count(dat_post, rmale) %>% arrange(desc(n))

count(dat_post, rsta) %>% arrange(desc(n))

dat_post %>% filter(rpostno <= 0) %>% select(post_id, rpostno)
```

## Join with resume level data

```{r}
# Rename variables in resume level data
dat_res <- dat_res %>%
rename(
    res_ptitle = ptitle,
    res_fname = fname,
    res_rname = rname
)

# Remove and rename variables in post level data
dat_post <- dat_post %>%
select(-c(pcat, pcity)) %>%
rename(
    post_ptitle = ptitle,
    post_fname = fname,
    post_rname = rname
)

# Join data
dat <- dat_res %>%
left_join(
    dat_post,
    by = "post_id",
    relationship = "many-to-one"
)

# Fill missing values in post level data from resume level data
dat <- dat %>%
mutate(
    post_ptitle = coalesce(post_ptitle, res_ptitle),
    post_fname = coalesce(post_fname, res_fname),
    post_rname = coalesce(post_rname, res_rname)
)

# Correct errors in recruiter gender identification
dat <- dat %>%
mutate(
    rmale = case_when(
        str_detect(post_rname, "先生") & (!rmale == "yes" | is.na(rmale))
        ~ "yes",
        str_detect(post_rname, "女士") & (!rmale == "no" | is.na(rmale))
        ~ "no",
        TRUE ~ rmale
    )
)
```

## Check for `rname` and `rmale` consistency

```{r}
# Gender identification with no name
dat %>%
filter(is.na(post_rname), !is.na(rmale)) %>%
select(post_id, post_rname, rmale)

# No gender identification with names
dat %>%
filter(!is.na(post_rname), is.na(rmale)) %>%
select(post_id, post_rname, rmale) %>%
distinct(post_id, post_rname, rmale)

# Check for gender consistency
dat %>%
filter((str_detect(post_rname, "先生") & (!rmale == "yes" | is.na(rmale))) |
(str_detect(post_rname, "女士") & (!rmale == "no" | is.na(rmale)))) %>%
select(post_id, post_rname, rmale)
```

## Check for inconsistencies in `ptitle` and `fname`

```{r}
dat %>%
filter(res_ptitle != post_ptitle) %>%
select(post_id, res_ptitle, post_ptitle)

dat %>%
filter(res_fname != post_fname) %>%
select(post_id, res_fname, post_fname)
```